A Flexible Space-time Tradeoff on Hybrid Index with Bicriteria Optimization

### 2016-09-28 manuscript.tex
another bug in Figure 1 found, an annotation for edge in sssp is missing now it suffices to be submitted to WWW

\numberofauthors{4} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
%AUTOR
%%% 1st. author
%\alignauthor Xingshen Song\\
%\affaddr{College of Computer}\\
%\affaddr{National University of Defense Technology}\\
%\affaddr{Changsha, China}\\
%\email{songxingshen@nudt.edu}
%% 2nd. author
%\alignauthor Yuexiang Yang\\
%\affaddr{College of Computer}\\
%\affaddr{National University of Defense Technology}\\
%\affaddr{Changsha, China}\\
%\email{yyx@nudt.edu}
%% 3rd. author
%\alignauthor Kun Jiang\\
%\affaddr{School of Electronic and Information Engineering}\\
%\affaddr{Xi'an Jiaotong University}\\
%\affaddr{Xi'an, China}\\
%\email{jk\_365@126.com}
%\and  % use '\and' if you need 'another row' of author names
%% 4th. author
%\alignauthor Yu Jiang\\
%\affaddr{College of Computer}\\
%\affaddr{National University of Defense Technology}\\
%\affaddr{Changsha, China}\\
%\email{jiangyu@nudt.edu}
%AUTHOR
}
\date{12 July 2016}

@@

>>>>

\numberofauthors{4} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
%AUTOR
%% 1st. author
\alignauthor Xingshen Song\\
\affaddr{College of Computer}\\
\affaddr{National University of Defense Technology,}
\affaddr{Changsha, China}\\
\email{songxingshen@nudt.edu}
% 2nd. author
\alignauthor Yuexiang Yang\\
\affaddr{College of Computer}\\
\affaddr{National University of Defense Technology,}
\affaddr{Changsha, China}\\
\email{yyx@nudt.edu}
%% 3rd. author
%\alignauthor Kun Jiang\\
%\affaddr{School of Electronic and Information Engineering}\\
%\affaddr{Xi'an Jiaotong University}\\
%\affaddr{Xi'an, China}\\
%\email{jk\_365@126.com}
%\and  % use '\and' if you need 'another row' of author names
%% 4th. author
%\alignauthor Yu Jiang\\
%\affaddr{College of Computer}\\
%\affaddr{National University of Defense Technology}\\
%\affaddr{Changsha, China}\\
%\email{jiangyu@nudt.edu}
%AUTHOR
}
\date{12 July 2016}

@@

\section{title}\label{sec: variable_size}
%Intuitively, fixed-sized blocks are not optimal for partitioning.
%To take things one step further,
There is a common view that splitting posting list into fixed-sized blocks is trend to be suboptimal, since integers are not expected to be  uniformly distributed along the list, a mandatory split makes the compressed size vulnerable to outliers inside the block.
Using variable-sized blocks can effectively improve the situation for it not only reduces the space occupancy, but also the number of blocks in the whole index, thus, we can expect a more efficient skipping when processing user queries.
However, arbitrarily dividing a posting list can be prohibitive due to the following reasons.
First, the edge complexities of DAG grow larger by introducing variable-sized blocks,
